---
title: "GetLipkinData"
author: "Dorothy Bishop"
date: "2024-04-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
```

## Where to find stuff
Data downloaded from https://figshare.com/articles/dataset/LanA_Dataset/20425209

SPM Subjects

Data paper is here: https://www.nature.com/articles/s41597-022-01645-3


The mirror analyses need Matlab. This is found on:
dorothybishop\Applications 

Type spm

Select fMRI

Modified version of mirror.m for Lipkin settings
outpth =
    '/Volumes/Extreme_Pro/_fedorenko_data/_mirrorout'

Have made script that works!

Need to read demographics bits

```{r readdemog}
outpth <-
    '/Volumes/Extreme_Pro/_fedorenko_data/_mirrorout'
rawfilepath <- 
    "/Volumes/Extreme_Pro/_fedorenko_data/assets/language/subjects"
    
filelist <- list.files(rawfilepath)
getbits <-read.table(paste0(rawfilepath,"/001/Demograhics_&_Summary.txt"))
df <-data.frame(matrix(NA,nrow=length(filelist),ncol=nrow(getbits)))
names(df)<-getbits[,1]

for (f in 1:length(filelist)){
  getbits <-read.table(paste0(rawfilepath,"/",filelist[f],"/Demograhics_&_Summary.txt"))
  df[f,]<-getbits[,2]
}

write.csv(df,paste0(outpth,'/demogs.csv'),row.names=F)
table(df$Handedness,df$Lateralization)
```


Lipkin2.csv was created in matlab to give mirror scores for 4 ROIs.
We'll try to do plots of these

```{r makedf}
datapath <- '/Volumes/Extreme_Pro/_fedorenko_data/_mirrorout/'
mydemog <- read.csv(paste0(datapath,'demogs.csv'))
mymirror <- read.csv(paste0(datapath,'lipkin2.csv'))
mydf<-rbind(mydemog,mydemog,mydemog,mydemog)
mydf<-cbind(mydf,mymirror)
mydf$Rhand <-1
mydf$Rhand[mydf$Handedness !='right']<-0
mydf$Rhand[mydf$Handedness =='NaN']<-NA
mydf$siglat <- 0
mydf$siglat[mydf$diff_CIlow>0]<- 1
mydf$siglat[mydf$diff_CIhigh<0] <- 1

table(mydf$Rhand,mydf$siglat,mydf$mask)

```

```{r makeplatestack}

mymasks<-c("frontal"  ,  "temporal" ,  "parietal" ,  "cerebellar" )
mycols<-c('black','red')
for (m in 1:length(mymasks)){
  thismask<-mymasks[m]
  myf<-filter(mydf,mask==thismask)
  myf<-myf[!is.na(myf$Rhand),]
  myf <- myf[order(myf$Rhand,myf$meandiff),] #because of missing data need to set rows nonautomatically
  t<-table(myf$Rhand) #Ns 
  v<-as.vector(t)
  lv <- length(v)
  rowlist<-vector()
  for (l in 1:lv){
    rowlist<-c(rowlist,1:v[l])
  }
  myf$row<-rowlist

  g<-ggplot(myf,aes(y=row,x=meandiff,col=(1+siglat)))+
  geom_point(size=.5,color=mycols[(1+myf$siglat)])+
  xlab("Mirror laterality index")+
  ylab("Rank order")+
  geom_errorbar(aes(xmin=diff_CIlow, xmax=diff_CIhigh),  width=.05,color=mycols[1+myf$siglat])+
  geom_vline(xintercept=0, linetype="dotted")+
    geom_vline(xintercept=mean(myf$meandiff),linetype="dashed")
  
g<-g+
  facet_grid(.~Rhand)+
    theme( axis.text = element_text( size = 12 ),
         axis.text.x = element_text( size = 10 ),
         axis.title = element_text( size = 12),
         title = element_text(size=16),
         legend.position="none",
         # The new stuff
         strip.text = element_text(size = 14))

plotname<-paste0('Lipkin_',thismask,'.png')
ggsave(here("plots",plotname),width=6,height=8)
}
```

```{r meansbyhand}

mya<- aggregate(mydf$meandiff,by=list(mydf$mask,mydf$Rhand),FUN=mean)
mys<- aggregate(mydf$meandiff,by=list(mydf$mask,mydf$Rhand),FUN=sd)
myn<- aggregate(mydf$meandiff,by=list(mydf$mask,mydf$Rhand),FUN=length)
mya<-cbind(mya,mys[,3],myn[,3])
dfmeans <- mya[1:4,]
dfbit<-mya[5:8,]
dfmeans<-cbind(dfmeans,dfbit)
dfmeans<-dfmeans[,c(1,10,8,9,5,3,4)]
names(dfmeans) <- c('mask','N RH','mean RH','sd RH','N nonRH','mean nonRH','sd nonRH')

```
